### 2021-07-04 code/manuscript.Rmd
Small fixes

# Read evoked *potentials* for all subjects
ave = [f"data/preprocessed/{sub}_ave.csv" for sub in r.subject_id]
ave = [pd.read_csv(fname) for fname in fname_ave]
ave = pd.concat(ave)

@@

# Read evoked *power* for all subjects
ave_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in r.subject_id]
ave_tfr = [pd.read_csv(fname) for fname in fname_ave_tfr]
ave_tfr = pd.concat(ave_tfr)

>>>>

# Read evoked *potentials* for all subjects
fnames = [f"data/preprocessed/{sub}_ave.csv" for sub in r.subject_id]
ave = [pd.read_csv(fname) for fname in fnames]
ave = pd.concat(ave)

@@

# Read evoked *power* for all subjects
fnames_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in r.subject_id]
ave_tfr = [pd.read_csv(fname) for fname in fnames_tfr]
ave_tfr = pd.concat(ave_tfr)
